Unity in diversity: shared basic social-cognitive processing in children from from 17 diverse communities

### 2024-01-31 paper/paper.Rmd
update supplement

```{r data}
data <- read_csv("../data/gafo-cc-clean-data.csv")%>%
  mutate(continent = ifelse(
    community %in% c("leipzig", "plymouth"), "Europe", 
    ifelse(
      community %in% c("akure", "hai||om", "khwe", "chimfunshi", "bandongo", "bayaka", "windhoek", "uganda"), "Africa",
      ifelse(community %in% c("stanford", "mexico", "buenos_aires"), "America",
             ifelse(community %in% c("india", "beijing", "turkey"), "Asia", "Oceania"))
    )
  ))%>%
  mutate(continent = factor(continent, levels = c("America", "Africa", "Europe", "Asia", "Oceania"), ordered = T))%>%
  mutate(community = recode(community,
                            akure = "Akure (Nigeria)",
                            leipzig = "Leipzig (Germany)",
                            `hai||om` = "Hai||om (Namibia)",
                            khwe = "Khwe (Namibia)",
                            windhoek = "Windhoek (Namibia)",
                            stanford = "Stanford (USA)",
                            chimfunshi = "Chimfunshi (Sambia)",
                            mexico = "Ocuilan (Mexico)",
                            plymouth = "Plymouth (UK)",
                            beijing = "Beijing (China)", 
                            india = "Pune (India)",
                            buenos_aires = "Buenos Aires (Argentina)",
                            auckland = "Auckland (New Zealand)",
                            turkey = "Malatya (Turkey)",
                            bandongo = "Bandongo (Rep. Congo)",
                            bayaka = "BaYaka (Rep. Congo)", 
                            uganda = "Nyabyeya (Uganda)"))
```

@@

>>>>

```{r data}
data <- read_csv("../data/gafo-cc-clean-data.csv")%>%
  mutate(continent = ifelse(
    community %in% c("leipzig", "plymouth"), "Europe", 
    ifelse(
      community %in% c("akure", "hai||om", "khwe", "chimfunshi", "bandongo", "bayaka", "windhoek", "uganda"), "Africa",
      ifelse(community %in% c("stanford", "mexico", "buenos_aires"), "Americas",
             ifelse(community %in% c("india", "beijing", "turkey"), "Asia", "Oceania"))
    )
  ))%>%
  mutate(continent = factor(continent, levels = c("Americas", "Africa", "Europe", "Asia", "Oceania"), ordered = T))%>%
  mutate(community = recode(community,
                            akure = "Akure (Nigeria)",
                            leipzig = "Leipzig (Germany)",
                            `hai||om` = "Hai||om (Namibia)",
                            khwe = "Khwe (Namibia)",
                            windhoek = "Windhoek (Namibia)",
                            stanford = "Stanford (USA)",
                            chimfunshi = "Chimfunshi (Zambia)",
                            mexico = "Ocuilan (Mexico)",
                            plymouth = "Plymouth (UK)",
                            beijing = "Beijing (China)", 
                            india = "Pune (India)",
                            buenos_aires = "Buenos Aires (Argentina)",
                            auckland = "Auckland (New Zealand)",
                            turkey = "Malatya (Türkiye)",
                            bandongo = "Bandongo (Rep. Congo)",
                            bayaka = "BaYaka (Rep. Congo)", 
                            uganda = "Nyabyeya (Uganda)"))
```

@@

Based on this, we also computed the number of older children living in the household. We did not pre-register this, but decided to also include this variable because prior work on advanced forms of social cognition has suggested that the presence of older siblings is slightly more predictive of development compared to other aspects of household composition [e.g., @lewis1996social; @ruffman1998older; but see @peterson2003opening]. We think that gaze following improves though practice during social interaction. Particularly supportive, we believe, are situations in which it is difficult to infer the goals and intentions of another person based on other information sources (e.g., language or context). In such situations, children have to pay closer attention to the interaction partner and use their gaze to make such inferences. We are well aware that the numbers in the questionnaire are very far removed from these forms of social interaction. Thus, at best, they are a very coarse approximation. As a consequence, we do not expect there to be a very strong link between the two. We sincerely hope that future work will be able to directly assess children's social interactions.
